\section{Definitions}
\begin{description}
    \item[Equal Error Rate (EER)] \label{def:EER} Metric used to evaluate the performance of a system. It represents the point at which the system's \hyperref[def:FAR]{false acceptance rate (FAR)} equals its \hyperref[def:FRR]{false rejection rate (FRR)}. A lower EER indicates a more accurate and reliable system as it signifies a balanced trade-off between security (minimizing FAR) and usability (minimizing FRR)

    \item[False Positive Rate (FPR)] \label{def:FPR} This is the probability of incorrectly accepting an unauthorized user

    \item[False Negative Rate (FNR)] \label{def:FNR} This is the the probability of incorrectly rejecting an authorized user

    \item[Hash Function] \label{def:Hash_Function} A hash function is an algorithm that converts input data of any size to a smaller fixed-size string of characters, which typically acts as a data fingerprint. The output, known as a hash, is unique for different inputs in ideal cases, making hash functions crucial for cryptography, data integrity, and indexing in databases.

    \item[Fuzzy Extractors] \label{def:Fuzzy_Extractors} Fuzzy extractors are cryptographic tools designed to reliably and securely generate a consistent, reproducible cryptographic key from biometric data or other noisy inputs that are inherently inconsistent. They enable the extraction of a stable key from an input that may vary slightly over different measurements, ensuring that even with minor variations, the same key can be reliably regenerated. This process typically involves two main components: a generator that produces a stable key and some public data from an initial input, and a reproducer that can regenerate the original key from a similar but not identical input using the public data.

    \item[Uniform Distribution] \label{def:Uniform Distribution} A uniform distribution signifies that each outcome within a set has an equal chance of occurring. In the context of finger vein patterns, it means any bit \(i\) in the biometric capture, representing either the presence or absence of a vein, is equally likely to be selected for analysis.

    \item[Hamming Distance] \label{def:Hamming Distance} The number of positions at which two biometric strings of equal length differ. It measures the similarity between the strings, with a lower distance indicating higher similarity.

    \item[Hamming Weight] \label{def:Hamming Weight} The number of 1's in a biometric string, indicating the presence of veins.

    \item[AES in CTR mode] \label{def:AES CTR mode} AES in Counter (CTR) mode is an encryption method that transforms a block cipher into a stream cipher. It achieves this by encrypting sequential counter values using AES. Each counter value is unique for each block of data, typically starting from an initial nonce (number used once) and incremented for subsequent blocks. This encryption method is traditionally used to encrypt data by generating a sequence of encrypted counters, which are then XORed with plaintext to produce ciphertext, allowing for encryption of arbitrary-sized data without padding. However, in the context of fuzzy hashing for biometric matching, AES-CTR is repurposed to generate a pseudorandom sequence, not for encrypting data but for selecting specific indices from a biometric template. This application leverages AES-CTR's cryptographic strength to ensure unpredictability and determinism in the selection process.

    \item[SHA-256 Hash] \label{def:SHA-256} SHA-256 is a cryptographic hash function in the SHA-2 family that produces a fixed-size 256-bit (32-byte) hash value from an input of arbitrary length. It has three fundamental properties: pre-image resistance, making it computationally infeasible to reverse the hash to find the original input; second pre-image resistance, preventing the discovery of a different input producing the same hash as a given input; and collision resistance, making it highly unlikely to find two different inputs that yield the same hash output. These properties ensure data integrity and security across various digital applications.

\end{description}
